---
title: "Homework 1"
author: Hilina Giday 
date: 9/24/2022
output: github_document
---

# Problem 1 

```{r}
library(tidyverse)
```

# Installing and Describing Penguins Data 

```{r}
data("penguins",package = "palmerpenguins")

```

In the dataset penguins there are `r nrow(penguins)` rows and `r ncol(penguins)` columns.
Each row represents a penguin's  species type, island location, bill length (mm), bill depth (mm), flipper length (mm), body mass (g), sex (m/f) and year. 


The mean flipper length is `r round(mean(pull(penguins,flipper_length_mm),na.rm = TRUE))` mm, while the maximum value for flipper length is `r max(penguins[,5], na.rm = TRUE)` mm and the minimum flipper length is `r min(penguins[,5],na.rm = TRUE)` mm.


# Creating a Scatterplot 

```{r scatterplot}

myplot2 = 
  ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm,col = species)) + geom_point() 

ggsave("myplot2.pdf",myplot2)

```


# Problem 2 

# Creating a New Dataframe

```{r}
third_df = tibble(
  norm = rnorm(10),
  logical = norm > 0, 
  vec_char = c("one","two","three","two","one","one","two","one","two","three"),
  vec_fac = factor (c("one","two","three","one","two","three","one","one","two","three"),
                    levels = c("one", "two", "three" ))
)
```

# Taking Means of Each Variable 

```{r}
mean(pull(third_df,norm))
mean(pull(third_df,logical))
mean(pull(third_df,vec_char))
mean(pull(third_df,vec_fac))
```

Simply pulling the column from the dataset and getting the mean was successful for the **normally distributed variable** and **logical vector variable**.For the  normally distributed values it was able to take the mean of that column because they were all in numeric format. However, for the logical vector column it took a different approach because they were characters, because a mean can't be taken of characters, it labeled them either as "0" or "1". Then, for the mean it was able to give a value and this value can be interpreted as a proportion. 

Unlike the **character vector variable** or for the **factor vector variable** which R does not label them as numeric values but just say's "NA" because it can not take the mean of character values.

# Converting variables into Numeric Values  

```{r setup, warning = FALSE, echo = T, results = 'hide'}
mean(as.numeric(pull(third_df,logical)))

mean(as.numeric(pull(third_df,vec_char)))

mean(as.numeric(pull(third_df,vec_fac)))

```

When we code to convert these variables into numeric values, R is able to do it successfully for the **logical vector variable** and the **factor vector variable**. The same method is used to explain what's happening to the logic vector column, it is being assigned numeric values and interpreted as a proportion. 

For the **factor vector variable**, it was able to also assign numeric values based on how we ranked the levels, unlike the **character vector variable** which doesn't have levels so R wasn't able to provide numeric values and therefore kept it character values and was not able to take the mean. 


