---
title: "Homework 1"
output: github_document
---

# Problem 1 

```{r}
library(tidyverse)

library(dplyr)
```

# Installing and Describing Penguins Data 

```{r}
data("penguins",package = "palmerpenguins")

```

```{r}
nrow(penguins)

ncol(penguins)

head(penguins)

round(mean(pull(penguins,flipper_length_mm),na.rm = TRUE))
```
In the dataset `penguins` there are **344 rows** and **8 columns**. Each row represents a penguin's  species type, island location, bill length (mm), bill depth (mm), flipper length (mm), body mass (g), sex (m/f) and year. For this dataset the mean flipper length is **201 mm**. 

# Creating a Scatterplot 

```{r scatterplot}

myplot2 = 
  ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm,col = species)) + geom_point() 


ggsave("myplot2.pdf",myplot2)
```

# Problem 2 

# Creating a New Dataframe

```{r}
third_df = tibble(
  norm = rnorm(10),
  logical = norm > 0, 
  vec_char = c("one","two","three","two","one","one","two","one","two","three"),
  vec_fac = factor (c("one","two","three","one","two","three","one","one","two","three"),
                    levels = c("one", "two", "three" ))
  
)
```

# Taking Means of Each Variable 

```{r}
mean(pull(third_df,norm))
mean(pull(third_df,logical))
mean(pull(third_df,vec_char))
mean(pull(third_df,vec_fac))
```

Simply pulling the column from the dataset and getting the mean was successful for the **normally distributed variable** and **logical variable**.For the  normally distributed variable it was able to take the mean of that column because it contained all numeric. However, for the logical variable it took a different approach because they are characters, it gave a value for each character value for example, labeling it a "0" or "1" : either it is there or it is not. Then, for the mean it was able to give a value because it treated the values as proportions. 

Unlike the **vector variable** or a **factor variable** which R does not try to give other numeric values to but just say's "NA" because it can not take the mean of character values.
